---
title: "Day 4 Part 2 Exploring Data"
author: "Dalila Lara"
format: html
editor: visual
---

These lines of code are specific to quarto to remove any code to not appear in rendering file output.

```{r}
#| warning: false
#| echo: false 
library(tidyverse)
library(palmerpenguins)
library(GGally)
library(skimr)
```

## Exploratory Data Visualization 

### Check out data a bit: 

The line of code below runs code to store objects if created put does not render on output

```{r}
#| include: false

# Tell me the column names 
names(penguins)

# What are the dimensions?
dim(penguins)

# Can you show me the first 6 lines?
head(penguins)

# Can you show me the last 6 lines?
tail(penguins)
```

Shows output but does not show code

```{r}
#| echo: false
2 + 10
```

Other options exist where user can click (code folding) to see code.

### Quick summary of data with skim() function

-   Mean

-   Percentile

-   Mini histogram

```{r}
skim(penguins)
```

### Large matrix of information

-   several diffferent graphs for species

-   quick overview summary for every variable on a data set

```{r}
# GGally::ggpairs(penguins)
```

## Jitterplot 

Flipper length by species

alpha = opacity

Can custom color by entering line of code scale_color_manual

Adding box plot to geom plot

```{r}
#| Fig = "My awesome figure caption"
ggplot(data = penguins, aes(x = species, y = flipper_length_mm)) + 
  geom_jitter(width = 0.2, 
              alpha = 0.5,
              height = 0,
              aes(color = species)) +
  geom_boxplot(fill = NA) +
  theme_light() +
  scale_color_manual(values = c("darkorchid4", "cyan4", "goldenrod")) +
  labs(x = "Penguins Species", y = "flipper length (mm)", title = "Palmer Penguins")
```

## Histogram 
only one variable

```{r}
ggplot(data = penguins, aes(x = bill_length_mm)) +
         geom_histogram(aes(fill = species), color = "magenta") + facet_wrap(~species, ncol = 1)
```
